---
title: "BST_682_HMWK_1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Question 1
```{r Question 1}
uber <- 3000
airbnb <- 1500
stata <- 800
women <- (uber * .30) + (airbnb*.45) + (stata * .65)
(uber *30) / women
```


###Question 2
```{r Question 2}
tails.distr.df <- data_frame(value = c(0,1,2,3,4), prob= c(1/16, 1/4, 3/4, 1/4, 1/16))
tails.distr.df
```

```{r Question 2 graph, echo= FALSE}

tails.distr.df %>% ggplot(aes(x=value, y=prob)) + geom_bar(stat = "identity") + ylim(c(0,1)) + xlab("X - Number of Tails") + ylab("f(X) Probability")

```

###Question 3
```{r Question 3 Data, echo=FALSE}
F <- c(18,31,34,33,27,33,28,23,33,12,19,25,14,4,22,7)
M <- c(11,22,27,29,24,29,25,26,38,14,23,31,20,6,34,12)
Y <- F
N <- F + M
```


```{r Question 3a, echo=False}
Y / N
```

```{r Question 3b, echo=False}
logL <- function(p) sum(log(dbinom(Y, N, p)))
optimize(logL, lower=0, upper=1, maximum=TRUE)

```


###Question 4
```{r Question 4}
year1 <- pnorm(55, mean = 40, sd=4, lower.tail = FALSE)  
year1 ^ 7
```


###Question 5
```{r Question 5}
Table_2_3_Birthweight_and_gestational_age$xy <- (Table_2_3_Birthweight_and_gestational_age[,2] * Table_2_3_Birthweight_and_gestational_age[,1])

Table_2_3_Birthweight_and_gestational_age$x_squared <- (Table_2_3_Birthweight_and_gestational_age[,1]^2)  

Table_2_3_Birthweight_and_gestational_age$y_squared <- (Table_2_3_Birthweight_and_gestational_age[,2]^2) 

sum_gage <- colSums(Table_2_3_Birthweight_and_gestational_age[,1])

sum_bwt <- colSums(Table_2_3_Birthweight_and_gestational_age[,2])

sum_xy <- colSums(Table_2_3_Birthweight_and_gestational_age[,4])

sum_x2 <- colSums(Table_2_3_Birthweight_and_gestational_age[,5])

sum_y2 <- colSums(Table_2_3_Birthweight_and_gestational_age[,6])

intercept_gage_bwt <- (((sum_bwt*sum_x2) - (sum_gage * sum_xy))) / ((((24 * sum_x2) - (sum_gage^2))))
intercept_gage_bwt

slope_gage_bwt <- ((24*sum_xy) - (sum_gage*sum_bwt)) / (((24*sum_x2) - (sum_gage^2)))
slope_gage_bwt
```


###Question 6

I use a book called Discovering Statistics using R. Online I use https://math.stackexchange.com
for the statistics questions, and https://stackoverflow.com for R programming questions. Mostly I use them because they are fairly easy to search through and ask a variety of questions with exhaustive responses.


###Question 7
```{r Question 7}
q7p1 <- ggplot(Table_2_3_Birthweight_and_gestational_age, aes(gestational_age, birth_weight, colour = sex))
q7p1 + geom_point()
xyplot(birth_weight ~ gestational_age|sex, data = Table_2_3_Birthweight_and_gestational_age)
```
Q7. Females have more weight diversity, makes have a sharper increase in weight by age than females.

###Question 8
```{r Question 8}
q8lm <- lm(formula = birth_weight ~ gestational_age, data= Table_2_3_Birthweight_and_gestational_age)
summary(q8lm)
```